# Non-Communicable Disease Burden (NCD)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the non-communicable diseases data
data_ncd <- read_csv(here("data", "burden-of-disease-ncd.csv"))
```

## Table of Estimates for NCD Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries 

ncd_burden <- read_csv(here::here("data/burden-of-disease-ncd.csv")) 

ncd_burden_clean <- burden_of_disease_cmnn %>% 
  rename(Country = 'Entity', DALYs = 'DALYs (Disability-Adjusted Life Years) - Communicable, maternal, neonatal, and nutritional diseases - Sex: Both - Age: Age-standardized (Rate)') %>% 
  filter(Country %in% c("Eritrea","Malawi","Japan"))

# You should pivot the data to show each country in a separate column.
ncd_burden_pivot <- ncd_burden_clean %>% 
pivot_wider(names_from = Country,
            values_from = DALYs)

# Use kable() from the knitr package to render the table.
knitr::kable(ncd_burden_pivot)
```

## Plot Showing Trends in NCD Burden Over Time 

```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
ncd_burden_plot <- ggplot(data = ncd_burden_clean,
                           mapping = aes(x = Year,
                                         y = DALYs,
                                         color = Country)) +
                                        geom_line()

print(ncd_burden_plot)
```

## Summary of NCD Burden Findings

Provide a brief analysis based on the data presented in the table and chart. Highlight any significant findings or patterns. About 3 sentences.
Malawi's variation in non-communicable diseases seems to spike upwards 1995 to 1998, then drop drastically downwards afterwards. Comparatively, Eritrea has a steady decline of DALYs from 1990 to 2020, while Japan's seems to remain stable year-to-year.


